{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-12-11 documents/brillouin_pulse_math.tex
No analytic solution
Replicated Z,C's result using functionalDerivative! yay

This problem is called "optimal control"?

>>>>

The Euler-Lagrange equation is usually brought up in the case of the Brachistochrone problem, or the Principle of Least Action (see Feynman lectures). In this case, the path through space, endpoints a to b, where space would seem to be replaced with the frequency domain.

Aha! That's the ticket!

Search terms: "first variation", gateaux derivative,
